### 2018-07-11 Stickleback_Paper.tex
Finished cleaning up results

Migration Rate | Introgression = ?

@@

If selection on SGV is key in rapid adaptation, 
many questions are exposed concerning the surrounding population genetics parameters and underlying genomic architecture.
How rapidly can selection act on standing genetic variants at a given value of migration, $M$?
How many alleles underly a certain trait? (expand here)
Furthermore, how can we infer causal loci for regions of the genome that must be driving the rapid adaptation, from real data.
Many biologist today make use of genome wide association studies (GWAS) and 
$F_{st}$ across the genome to estimate regions responsible for certain traits. 
Unfortunately, the data can be heavily influenced by the level of introgression and population structure of the samples. 
This being the case, what are the biases we can expect to see in real data for certain levels of introgression.

There are many different parameters that carry a large impact on the questions above.
\citet{Ralph2015} 
explored the dichotomy of selection on new alleles and those brought in by migrants from a similar selective pressure.
This lead to an understanding of the process by which alleles move from an existing 'patch' to an introduced 'patch' with the 
same selective pressure. 
%read though Peter's paper more and connect it to what we're doing here.

@@

Here, we're interested in observing how different parameter values
(mainly migrations rates and recombination rates)
impact the sharing of alleles between populations. 
%\plr{Below, I think we should make sure to use ``population'' to mean either ``lake'' or ``ocean'';
%    so when we compute freshwater-marine $F_{ST}$ this measures differentiation between habitats,
%    not between populations.}
We define pre-existing freshwater adapted alleles at time $t$,
%\plr{I vote to remove the abbreviations. Also, should make the dependence on generation more clear: maybe ``freshwater adapted alleles at time $t$''?} 
to be a mutations with a frequency higher than $0.5$ in \textit{any} of the original lakes, 
while remaining lower than $0.5$ in the marine. 
They are defined this way because the transportation hypothesis does not specify where or when an advantageous mutation arises,
but simply suggests that when a freshwater adapted alleles comes to high enough frequency, it too, could participate in the transportation process \cite{schluter2009genetics}.
To observe transportation of freshwater alleles in our simulations, we use a variety of metrics when sampling.
let $P_{1}$ and $P_{2}$ be the vector of mutation frequencies in the first and second populations, respectively.
with $\hat{P} = (P_{1} + P_{2}) / 2$ and
$PQ = (P_{1} \times (1 - P_{1}) + P_{2} \times (1 - P_{2})) / 2$,
we compute $F_{ST} = 1 - (PQ / (\hat{P} \times (1 - \hat{P})))$.
%mean number of original lakes each FAA appears in,
%and total number of unique FAA. 
Time to adaptation ($T_{adapt}$) of the introduced population is the generation at which
the difference between the average phenotype of the original and the introduced freshwater populations is less than 0.5. 
To understand where, as well as how much, of these pre-existing freshwater adapted alleles are being transported,
we track the the average percentage of freshwater adapted alleles at time $t$ across all populations throughout the simulation.
%\plr{Here FAA are defined in terms of the original populations, explaining why the introduced populations can have MPFAI of 0.
%    This is counter-intuitive from the name (FAA); maybe we should call them ``pre-existing freshwater alleles''?
%    ``standing genetic variants''?}
%we're particularly interested in using MPFAI to measure the marine population' capacity to carry FAA,
%as well as observing the introduced populations' ability to select upon them. 
%\plr{omit this last sentence?}
%Because we are interested in the local adaptation of the introduced freshwater populations,

@@

Across a range of introgression from $\approx 0.01 - 100.0$ migrants per generation in populations of 
size 2000 diploid individuals, we encountered large influence on 
time to adaptation,
sharing of pre-existing freshwater adapted alleles,
and population genetic signals left behind in the simulated populations.
A larger amount of introgression from all lakes to the marine population helped both the initial and introduced freshwater populations 
share pre-existing freshwater adapted alleles.
this resulted in rapid adaptation ($\approx 100$ generations) of the introduced population to adapt to the freshwater environment.
We also found that larger amounts of migration allow for more statistical power and less false positives in the resulting population genetics data ($F_{st}$ per SNP across the genome).

%We found this
%--justify it

% A LIST OF PLOTS
% GENERAL OBSERVATIONS

% [1]. Fst Neutral 
% [2]. Fst Effect 
% [3]. Fst Across The 
% [4]. Median Number of FAA Per individual / Total Number of FAA
% [5]. Phenotype Distribution
% [6]. Percentage of shared High Frequency Alleles Shared Between Original and Introduced
% [7]. Correlation of Allele Frequency 
% [8]. Time until Adaptation
% [9]. Total Num FWAA - Average number of lakes each allele appears in.
% [10]. Distribution of # of FWAA Per marine individual.

@@

Local adaptation occurred across all simulated parameter values.
Starting from the same baseline, freshwater and marine populations diverged phenotypically
until they reached an equilibrium
where the population means were close to or at the optimal phenotype. 
phenotypic variation within each population was small compared to the difference between populations.
Polymorphic loci that affected the phenotype,
showed greater differentiation compared to neutral loci between marine and freshwater populations, 
with the exception of the lowest migration rate of 0.01 migrants per generation per lake. 
%$F_{st}$ plots along the genome, show peaks at loci underlying local adaptation.

%\plr{Rather than referring to e.g., ``migration rate of $5 \times 10^{-5}$'',
%    it'd be easier to follow if we had names for the different migration rate situations.
%    Maybe ``low, medium-low, medium-high, and high''?
%    Or talk about the number of migrants per generation per lake, e.g.,
%    ``with the exception of the lowest migration rate of 0.01 migrants per generation per lake''?}

\todo{ add more general observations and caveats about not all parameter values. }

\plr{It would be nice to have a small table of parameter values,
    so that when someone wonders ``What was the population size again?'' they could easily find it.}
\jgg{Re: agreed}

%\plr{I vote to put figures \ref{fig:phenotype_ts2} and \ref{fig:phenotype_ts3} 
%    together as one figure and put them here.
%    There's a lot in those we could talk about: you can see the stepwise introduction
%    of individual alleles in figure \ref{fig:phenotype_ts2}, for instance.}

\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/PhenotypeThroughout5e-4.png}
  		\caption{ Average phenotype in each population as a function of time $t$, in generations. 
		This is a single simulation run at a migration rate of $5 \times 10^{-4} \approx 1$ mig/gen. 
		The dark black line represents the mean phenotype of the single marine population with an optimum trait value of + 10. 
		The pink represents the entire initial freshwater population mean, 
		as a sum of all the lakes (light green) with and optimum trait value of -10.
		The orange represents the entire introduced freshwater population mean
		as a sum of all the lakes (dark green) with an optimum trait value of -10 as well.
		}
  		\label{fig:phenotype_ts2}
	\end{center}
\end{figure}

\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/PhenotypeThroughout5e-3.png}
  		\caption{Average phenotype in each population as a function of time $t$, in generations. 
		This is a single simulation run at a migration rate of $5 \times 10^{-3} \approx 1$ mig/gen. 
		The dark black line represents the mean phenotype of the single marine population with an optimum trait value of + 10. 
		The pink represents the entire initial freshwater population mean, 
		as a sum of all the lakes (light green) with and optimum trait value of -10.
		The orange represents the entire introduced freshwater population mean
		as a sum of all the lakes (dark green) with an optimum trait value of -10 as well.
		}
  		\label{fig:phenotype_ts3}
	\end{center}
\end{figure}

\jgg{we should make one caption and the two above should be top-bottom sub-figures}
\jgg{also, interesting point to make on second plot, you can see the initial lakes taking the same size step. sharing}
%I could zoom in on the relevent portions of the figure for this. (begging and introduction)
% a 2 by 2 with the important sections (0 - 20K) $ (40-50K) for both above figures. share axes

\jgg{finished with most edits up to here}

\subsection*{The Effect of Migration Rate}

\subsubsection*{Migration homogenizes genetic variation}

@@

Across increasing parameters of migration, we observed more gene flow across the populations. 
As can be seen in Figure \ref{fig:Fst},
$F_{st}$ values for neutral alleles steadily decline between all sets of populations as 
migration increases, this illustrates less difference between sections of the genome which are not acted up 
upon by selection, in all populations.
Additionally, standing genetic variance
(seen in Figure \ref{fig:SGV})
values in the marine population steady increased with migration which suggests that more alleles from the 
lakes surrounding were exporting alleles into the marine individual.

@@

\subsubsection*{migration affects the speed of adaptation}

@@

We observed a dramatic shift in time until adaptation for the introduced populations
as migration rates increased. 
As can be seen in Figure \ref{fig:TimeToAdaptation} at the lowest migration rate of $5 * 10^{-5}$,
It took the introduced population over 20 thousand generations for the average phenotype of all the lakes to 
get to within 0.5 of the original lakes original phenotypes. 
%\plr{From the plots it looks more like adaptation happens (at least in most lakes) by like 10K or 15K.}
This suggests that selection was acting primarily on new mutations, meaning the 
introduced lakes needed to wait for a beneficial mutation to arise before 
it was selected upon. 
%\plr{We should do the calculation to see if this makes sense: 
%    there's one new effect mutation in the right direction every 100 generations in the lakes,
%    one of effect size $s$ has probability of about $s/2$ of not being lost to drift...}
There was a positive correlation between the amount of standing genetic variation in the 
marine and the rapid adaptation of the introduced populations.

@@

\subsubsection*{sharing of freshwater adapted alleles}

@@

To further investigate this correlation, we take a look at the FAA driving 
local adaptation of the introduced population. 
One common metric we investigate is the percentage of FAA per individual in each of the populations. 
This gives us a general look at the where these alleles are being distributed. 
Looking at the lowest migration rate for the original lakes population In Figure (MPAA / IND) 
We see that the average individual has almost exactly $1/10^{th}$ of the total defined FWAA throughout the simulation. 
Because FAA are defined among \textit{any} population, this suggests that each one of the $10$ 
lakes has created their own solution to adaptation of the the freshwater selective pressure.

As we can see in Figure (Total/Avg shared)
as migration rate parameter increases for the simulations, 
we see the distribution of the total number of FAA's decrease, and 
the average number of lakes each allele appears in at high frequency ($p > 0.5$), increase.
With the distribution of effect size remaining the same across all simulations, 
these are both suggestive of the original lakes sharing solutions to the same selective pressure.

@@

\subsubsection*{We see Migration Load after a certain threshold of migration}

@@

In the distributions we have shown across migration rate parameter values, 
We have experienced the most dramatic shifts of the population dynamics at $M = 5x10^{-3}$.
After a threshold between this and $M = 5x10^{-2}$, we start to experience migration load. 
Significant gene flow constricts local adaptation
as a consequence of a large number of offspring through hybridization events between subpopulations.
In Figure \ref{fig:MeanPhenotype} at $M = 5x10^{-2}$, we can see the distribution of average phenotype throughout the simulation
pull towards the opposing selective pressure value and away from the local optimum in all subpopulations.

@@

\subsubsection*{There is a Qualitative Threshold of migration rates}

%FIGURES THAT SHOW THIS:
%all
%TIES TO NATURE?
%SPECIFICALLY (interesting stuff)

%GENERAL
We have found that too little migration leads to selection upon new mutations in all subpopulations and lakes alike. 
In contrast, at high migration rates we have seen that migration load limits 
the ability for species to locally adapt to the selective pressure of their environment.
This leads us to consider a window (Goldilocks Zone) of introgression which allows for the transportation
of FAA's without migration load. In a species that commonly is subjected to two general types of selective pressure 
such as marine and 
\plr{Maybe this goes in the Discussion? Remaining observations could merge with the previous section.}

@@

\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/FstAcross5e-3.png}
  		\caption{(Decription and cleaning needed)
		}
  		\label{fig:Fst3}
	\end{center}
\end{figure}

\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/FstAcross5e-4.png}
  		\caption{(Description and cleaning needed)
		}
  		\label{fig:Fst2}
	\end{center}
\end{figure}

@@

%

Here, we take a closer look at the genomic architecture of local adaptation between freshwater and marine individuals. 
Often when looking at real datas, biologists observe patterns of $F_{st}$ and clustering of alleles that suggest causative loci for certain traits.
However, researchers would like to know how parameters such as migration and recombination impact the results from natural populations.
To give an idea about the impact of these parameters in our model, we examine the distribution, location, and false positive rate on predicting effect loci
given the $F_{st}$ per SNP across the genome.

\subsubsection*{False-Positives \& Statistical Power}

\plr{Start off by talking about Fst along the genome, then say ``if we identify QTL as the outliers, then...''}
\plr{I vote for combining and including figures \ref{fig:Fst2} and \ref{fig:Fst3}.}
Given that migration increases the gene flow between subpopulations, how valid are $F_{st}$ peaks at different $M$. 
Knowing exactly which mutations effect phenotype in our simulations, 
we can look at the statistical power and false positives given $F_{st}$ per SNP across the genome. 
In Figure \ref{fig:Power_FP} , looking at an $F_{st}$ threshold greater than 1, we see the two lowest migration rates $10^{-5}$ and $10^{-4}$ having very little statical power. 
This along with low false positive rate across all $F_{st}$ threshold values is fairly predictable when you consider the high $F_{st}$ values across the genome.

%The lowest migration rate of $10^{-5}$ also has a very low false positive rate across all $F_{st}$ threshold values.

%\subsubsection*{Low Recombination Causes Clustering}

@@

@@

%(1) There's a threshold of introgression for both rapid adaptation and migration load. 
\subsection*{thresholds}

%(2) Do the math, discuss number ( and possibly type ) of mutations underlying the trait value.
\subsection*{do the math}

@@

>>>>

Migration Rate | Historical Introgression = ?

@@

If selection on standing genetic variants is key in rapid adaptation, 
many questions are exposed concerning the surrounding population genetics parameters and underlying genomic architecture.
%How rapidly can selection act on standing genetic variants at a given value of migration, $M$?
What scale of historical introgression between populations with selective pressures $X$ and $Y$, allows for rapid and parallel local adaptation
of a population derived from $X$ to an introduced environment with selective pressure $Y$?
What is the origin of pre-existing adaptive variants?
How are the variants structured, historically and across the genome underlying the trait?
%How does population genetics data influenced by historical introgression and selection on standing genetic variants?
%How many alleles underly a certain trait and how many are swept away by drift? 
Furthermore, how can we infer causal loci for regions of the genome that must be driving the rapid adaptation, from real data.
Many biologists today make use of genome wide association studies (GWAS) and 
$F_{st}$ across the genome to estimate regions responsible for certain traits. 
Unfortunately, the data can be heavily influenced by the level of introgression and population structure of the samples. 
This being the case, what are the biases we can expect to see in real data for certain levels of introgression.

There are many different parameters that carry a large impact on the questions above.
\citet{Ralph2015} 
explored the dichotomy of selection on new alleles and those brought in by migrants from a similar selective pressure.
Answering the fundamental questions surrounding spatial resolution of convergent evolution. 
%This lead to an understanding of the process by which alleles move from an existing 'patch' to an introduced 'patch' with the 
%same selective pressure. 
\jgg{It seems like this could be a good parallel to what we're doing here, or maybe for discussion?}

@@

Here, we're interested in observing how different parameter values
(mainly migrations rates and recombination rates)
impact the sharing of alleles between populations. 
%\plr{Below, I think we should make sure to use ``population'' to mean either ``lake'' or ``ocean'';
%    so when we compute freshwater-marine $F_{ST}$ this measures differentiation between habitats,
%    not between populations.}
We define pre-existing freshwater adapted alleles at time $t$,
%\plr{I vote to remove the abbreviations. Also, should make the dependence on generation more clear: maybe ``freshwater adapted alleles at time $t$''?} 
to be a mutations with a frequency higher than $0.5$ in \textit{any} of the original lakes, 
while remaining lower than $0.5$ in the marine. 
They are defined this way because the transportation hypothesis does not specify where or when an advantageous mutation arises,
but simply suggests that when a freshwater adapted alleles comes to high enough frequency, it too, could participate in the transportation process \citep{schluter2009genetics}.
To observe transportation of freshwater alleles in our simulations, we use a variety of metrics when sampling.
let $P_{1}$ and $P_{2}$ be the vector of mutation frequencies in the first and second populations, respectively.
with $\hat{P} = (P_{1} + P_{2}) / 2$ and
$PQ = (P_{1} \times (1 - P_{1}) + P_{2} \times (1 - P_{2})) / 2$,
we compute $F_{ST} = 1 - (PQ / (\hat{P} \times (1 - \hat{P})))$.
%mean number of original lakes each FAA appears in,
%and total number of unique FAA. 
Time to adaptation ($T_{adapt}$) of the introduced population is the generation at which
the difference between the average phenotype of the original and the introduced freshwater populations is less than 0.5. 
To understand where, as well as how much, of these pre-existing freshwater adapted alleles are being transported,
we track the the average percentage of freshwater adapted alleles at time $t$ across all populations throughout the simulation.
%\plr{Here FAA are defined in terms of the original populations, explaining why the introduced populations can have MPFAI of 0.
%    This is counter-intuitive from the name (FAA); maybe we should call them ``pre-existing freshwater alleles''?
%    ``standing genetic variants''?}
%we're particularly interested in using MPFAI to measure the marine population' capacity to carry FAA,
%as well as observing the introduced populations' ability to select upon them. 
%\plr{omit this last sentence?}
%Because we are interested in the local adaptation of the introduced freshwater populations,

@@

Across a range of historical introgression from $\approx 0.01 - 100.0$ migrants per generation in populations of 
size 2000 diploid individuals, we encountered large influence on 
time to adaptation,
sharing of pre-existing freshwater adapted alleles,
and population genetic signals left behind in the simulated populations.
More gene flow is experienced with greater historical introgression between the two selective pressures.
Interestingly, the ability for separate populations to locally adapt to their own selective pressure was relatively unaffected 
until the highest rate of migration between the marine and freshwater environments.
All rates of historical introgression aside from the lowest, helped both the initial and introduced freshwater populations 
share pre-existing freshwater adapted alleles.
The sharing of alleles resulted in rapid adaptation ($\approx 100$ generations) of the introduced population (split from the marine population) to adapt to the freshwater environment.
We also found that larger amounts of migration allow for more statistical power and less false positives in the resulting population genetics data ($F_{st}$ per SNP across the genome).

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/PhenotypeThroughout5e-4.png}
  		\caption{ Mean individual trait value in each population as a function of time $t$, in generations. 
		This is a single simulation run at a migration rate of $5 \times 10^{-4} \approx 1$ mig/gen in both 
		directions for every freshwater population to the single marine population. 
		The dark black line represents the mean phenotype of the single marine population with an optimum trait value of + 10. 
		The pink represents the entire initial freshwater population mean
		of all the lakes (light green) with and optimum trait value of -10.
		The orange represents the entire introduced freshwater population mean
		of all the lakes (dark green) with an optimum trait value of -10 as well.
		}
  		\label{fig:phenotype_ts2}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/PhenotypeThroughout5e-3.png}
  		\caption{Mean individual trait value in each population as a function of time $t$, in generations. 
		This is a single simulation run at a migration rate of $5 \times 10^{-3} \approx 1$ mig/gen in both 
		directions for every freshwater population to the single marine population. 
		The dark black line represents the mean phenotype of the single marine population with an optimum trait value of + 10. 
		The pink represents the entire initial freshwater population mean
		of all the lakes (light green) with and optimum trait value of -10.
		The orange represents the entire introduced freshwater population mean
		of all the lakes (dark green) with an optimum trait value of -10 as well.
		}
  		\label{fig:phenotype_ts3}
	\end{center}
\end{figure}

\jgg{we should make one caption and the two above should be top-bottom sub-figures}
\jgg{also, interesting point to make on second plot, you can see the initial lakes taking the same size step. sharing}
%I could zoom in on the relevent portions of the figure for this. (begging and introduction)
% a 2 by 2 with the important sections (0 - 20K) $ (40-50K) for both above figures. share axes
%\jgg{finished with most edits up to here}

@@

Local adaptation occurred across all simulated parameter values.
Starting from the same baseline, freshwater and marine populations diverged phenotypically
until they reached an equilibrium
where the population means were close to or at the optimal phenotype. 
The distribution of mean number of freshwater adapted alleles suggested that there was 
$\approx 8$ SNPs underlying the freshwater phenotype. 
This was true for all rates of introgression except for the highest at $100$ mig/gen
where the mean trait value in the populations equilibrated well below the optimum.
We can see the introduction of new alleles in Figure \ref{fig:phenotype_ts2}. 
In generation (0 - 20K) The sweeps that cause jumps in the mean phenotype of the freshwater population 
have a relatively large effect size equal to or greater than $1$.
%In Figure \ref{fig:counts} we can see that the number of effect regions with zero 
%pre-existing freshwater adapted alleles increased with introgression while
%regions of effect containing more pre-existing freshwater adapted alleles increase.
Phenotypic variation within each population was small compared to the difference between populations.
Polymorphic loci that impact the individual trait value,
showed greater differentiation compared to neutral loci between marine and freshwater populations, 
with the exception of the lowest migration rate of 0.01 migrants per generation per lake.

\todo{ add more general observations and caveats about not all parameter values. }
\plr{It would be nice to have a small table of parameter values,
    so that when someone wonders ``What was the population size again?'' they could easily find it.}
\jgg{Re: agreed}

\subsection*{Migration homogenizes genetic variation}

@@

Across increasing parameters of migration, we observed more gene flow across the populations. 
As can be seen in Figure \ref{fig:Fst},
$F_{st}$ values for neutral alleles steadily decline between all sets of populations as 
migration increases, this illustrates less difference between sections of the genome which are not acted
upon by selection, in all populations.
Additionally, standing genetic variance
(seen in Figure \ref{fig:SGV})
values in the marine population steady increased with migration which suggests that more alleles from the 
lakes surrounding were exporting alleles into the marine individual.

@@

\subsection*{migration affects the speed of adaptation}

@@

We observed a dramatic shift in time until adaptation for the introduced populations
as migration rates increased. 
As can be seen in Figure \ref{fig:TimeToAdaptation} at the lowest migration rate of $5 \times 10^{-5}$,
It took the introduced population over 20 thousand generations for the mean trait value, $X_{I}$ of all the lakes to 
get to within 0.5 of the original lakes mean trait value, $X_{O}$
%\plr{From the plots it looks more like adaptation happens (at least in most lakes) by like 10K or 15K.}
This suggests that selection was acting primarily on new mutations, and that the 
introduced lakes needed to wait for a beneficial mutation to arise before 
it was selected upon. 
%\plr{We should do the calculation to see if this makes sense: 
%    there's one new effect mutation in the right direction every 100 generations in the lakes,
%    one of effect size $s$ has probability of about $s/2$ of not being lost to drift...}
There was a positive correlation between the amount of standing genetic variation in the 
marine and the rapid adaptation of the introduced populations.

%(2) Do the math, discuss number ( and possibly type ) of mutations underlying the trait value.
\subsection*{do the math}
\jgg{peter? :)}

@@

\subsection*{sharing of freshwater adapted alleles}

@@

To further investigate this correlation, we take a look at the freshwater adapted alleles driving 
local adaptation of the introduced population. 
One common metric we investigate is the percentage of freshwater adapted alleles per individual in each of the populations any time $t$. 
This gives us a idea of where the where these alleles are being distributed throughout the simulation run. 
Looking at the lowest migration rate for the original lakes population In Figure \ref{fig:MPFAI}
We see that the average individual has almost exactly $1/10^{th}$ of the total defined freshwater adapted alleles throughout the simulation. 
Because FAA are defined among \textit{any} population, this suggests that each one of the $10$ 
lakes has created their own solution to adaptation of the the freshwater selective pressure.

As we can see in Figure \ref{fig:NumFAA}
as historical introgression increases for the simulations, 
we see the distribution of the total number of freshwater adapted alleles decrease, and 
the average number of lakes each allele appears in at high frequency ($p > 0.5$), increase.
With the distribution of effect size remaining the same across all simulations, 
these are both suggestive of the original lakes sharing solutions to the same selective pressure.

@@

\subsection*{We see Migration Load after a certain threshold of migration}

@@

In the distributions we have shown across migration rate parameter values, 
We have experienced the most dramatic shifts of the population dynamics at $M = 5x10^{-3}$.
After a threshold between this and $M = 5x10^{-2}$, all populations begin to experience migration load. 
Significant gene flow constricts local adaptation
as a consequence of a large number of offspring through hybridization events between subpopulations.
In Figure \ref{fig:MeanPhenotype} at $M = 5x10^{-2}$, we can see the distribution of average phenotype throughout the simulation
pull towards the opposing selective pressure value and away from the local optimum trait value in all populations.

@@

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/FstAcross5e-3.png}
  		\caption{(Description and cleaning needed)
		}
  		\label{fig:Fst3}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/FstAcross5e-4.png}
  		\caption{(Description and cleaning needed)
		}
  		\label{fig:Fst2}
	\end{center}
\end{figure}

Now we take a closer look at the genomic architecture of local adaptation between freshwater and marine individuals. 
Often when looking at real datas, biologists observe patterns of $F_{st}$ and clustering of alleles that suggest causative loci for certain traits.
However, researchers would like to know how parameters such as migration and recombination impact the results from natural populations.
To give an idea about the impact of these parameters in our model, we examine the distribution, location, and false positive rate on predicting effect loci
given the $F_{st}$ per SNP across the genome.

@@

\subsection*{False-Positives \& Statistical Power}

%\plr{Start off by talking about Fst along the genome, then say ``if we identify QTL as the outliers, then...''}
%\plr{I vote for combining and including figures \ref{fig:Fst2} and \ref{fig:Fst3}.}

At higher rates of introgression in our simulations, we saw $F_{st}$ peaks at regions of the genome underlying individual trait value (phenotype). 
In contrast, the lower rates of introgression showed higher $F_{st}$ across the entire genome such that the regions under selection were indistinguishable. 
For every $F_{st}$ peak, we saw the same regions of the genome express high $F_{st}$ when comparing either the initial \textit{or} introduced freshwater populations to the marine population.
If we identify quantitative trait loci as the outliers, then this is again suggestive of both freshwater populations sharing regions of divergence from the marine population.

With 10 effect regions across the genome, we can see in \ref{fig:Fst3} that only about 1 or 2 of the region contain peaks. 
%SOFT STATEMENT - MORE (Peak) EVALUATION?
When looking closely at the peaks we see that each is usually a composition of 7-8 SNPs close in proximity.
%SOFT STATEMENT -
Because some of those mutations are selectively neutral (we can see this because the counts of FAA are not as high as the number in the clusters),
this is suggestive of hitchhiking alleles along with the SNPs being brought to high frequency by a selective sweeps.

In regions of the genome underlying individual trait value, we observed 
Given that migration increases the gene flow between subpopulations, how valid are $F_{st}$ peaks at different $M$. 
Knowing exactly which mutations effect phenotype in our simulations, 
we can look at the statistical power and false positives given $F_{st}$ per SNP across the genome. 
In Figure \ref{fig:Power_FP} , looking at an $F_{st}$ threshold greater than 1, we see the two lowest migration rates $10^{-5}$ and $10^{-4}$ having very little statical power. 
This along with low false positive rate across all $F_{st}$ threshold values is fairly predictable when you consider the high $F_{st}$ values across the genome.

%The lowest migration rate of $10^{-5}$ also has a very low false positive rate across all $F_{st}$ threshold values.
%\subsubsection*{Low Recombination Causes Clustering}

@@

We have shown that historical introgression, at our given parameter sets,
is able to reproduce rapid and parallel adaptation similar to what we've seen in real populations.
Selection is able to rebuild the freshwater haplotype from marine populations.
Almost all rates of migration were helpful in the efficiency of the population to locally adapt except for the highest at which migration load 
limited the ability of the populations to reach the local optimum.

We also have also explored the genomic architecture as a consequence of the nature of selection in our scenario. 
The alleles underlying individual trait value were of large effect and a low number. 
With a total of $10^{5}$ loci, to be realistic, each loci should represent 1000 $Kb$ in real data.

We have also shown introgression is beneficial for inferring causative loci from divergence ($F_{st}$) along the genome. 
%wouldn't it be cool if we could use this fact and simulate introgression, starting with real data that is noisy to extrapolate the areas we care about?
%this could be nonsense

@@

%(1) There's a threshold of introgression for both rapid adaptation and migration load. 
%(1.5) Maybe refer to the literature for migration load.  
\subsection*{thresholds}

We have found that too little migration leads to selection upon new mutations in all subpopulations and lakes alike. 
In contrast, at high migration rates we have seen that migration load limits 
the ability for species to locally adapt to the selective pressure of their environment.
This leads us to consider a window (Goldilocks Zone) of introgression which allows for the transportation
of FAA's without migration load. In a species that commonly is subjected to two general types of selective pressure 
such as marine and freshwater stickleback this is suggestive of the benefit of hybridization in all subpopulations before
reaching a point of pre or post zygotic

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=\linewidth]{matplotlibPlots/effectRegionCounts.png}
  		\caption{(PLACEHOLDER)}
		\label{fig:counts}
	\end{center}
\end{figure}
